Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-30 ms/manuscript.Rmd
Update manuscript

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology for two reasons: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on one metric, species richness. Much progress has been made documenting hotspots of exceptional species richness, the processes generating them, and enabling conservation strategies to preserve them. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.

Presumably, the main reason phylogeny has not been taken into account more promimently in biodiversity studies is because data (DNA sequences) and analytical tools have only become available relatively recently. These tools and datasets now make it possible to analyze other dimensions of biodiversity, such as phylogenetic diversity and phylogenetic endemism. Better ways to characterize biological regions ("bioregions") are also available, rather than relying on ad-hoc characterizations. Furthermore, incorporating these two frameworks---the categorization of areas into phyloregions with analysis of over/under dispersion of biodiversity---can provide particularly powerful insights into the processes structuring biodiversity and suggest conservation priorities.

>>>>

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology for two reasons: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on species richness. For example, hotspots, or areas of exceptionally high richness, have received particular attention, resulting in a widely-recognized set of 34 terrestrial hotspots and motivating conservation strategies to preserve them. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.

Presumably, the main reason phylogeny has not been taken into account more prominently in biodiversity studies is because data (DNA sequences) and analytical tools have only become available relatively recently. These tools and datasets now make it possible to analyze other dimensions of biodiversity, such as phylogenetic diversity and phylogenetic endemism. Better ways to characterize biological regions ("bioregions") are also available, rather than relying on ad-hoc characterizations. Furthermore, incorporating these two frameworks---the categorization of areas into phyloregions with analysis of over/under dispersion of biodiversity---can provide particularly powerful insights into the processes structuring biodiversity and suggest conservation priorities.
